\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
update eva: demand arrivals
testbed updated, sth TBD

\textbf{User demands arrive continuously.}
We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 miniutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes, where link failures occur probabilistically, 
and is repeated for 50 times.

%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
%Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.
\textit{Admission control.} We evaluate how demands can be correctly admitted by $\mathsf{BATE}$, 
comparing with both the optimal admission strategy, 
and a strategy that assumes a \textit{fixed} bandwith allocation for demands that have already been admitted, which is effectively step (1) in $\mathsf{BATE}$.
Figure \ref{e2}(a) demonstrates that $\mathsf{BATE}$ performs closely to the optimal strategy, 
i.e., the false rejection ratio is at most 1\%, while the \textit{fixed} algorithm 
rejects least 10$\times$ more admissible demands. 
%This is because $\mathsf{BATE}$ fully considers the availability diversity of tenants.
%In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwith availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in every second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfication, under 
different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
To further illustrate the difference in their mechanisms, 
we plot in Figure \ref{e2}(c), for each algorithm, the ratio of the allocated bandwidth 
to the demanded bandwidth. 
The cdf curve shows that FFC is too conservative in bandwidth allocation, 
which failes to allocate proper bandwidth in almost 60\% time.   
On the other hand, although TEAVAR provides bandwidth fairly well, 
it ignores the diverse availability requirements of different users, 
and achieves a lower satisfication ratio than $\mathsf{BATE}$.

\textit{Failure Recovery} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(d) plots the overall profit $\mathsf{BATE}$, FFC and TEAVAR can achieve for admitted demands, under three different admission control strategies, i.e., fixed, AD (which is the strategy $\mathsf{BATE}$ uses) and optimal. 
\textbf{TBD: This is because $\mathsf{BATE}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.}
Figure \ref{e2}(e) further depicts the fraction of profit loss caused by SLA violations, where the baseline for each algorithm is the profit it can achieve when no failures occur. 
\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation, as indicated in Figure \ref{e2}(c) earlier.

@@

\textbf{A private cloud example}

%In this part we will perform experiments on our testbed to evaluate the performance of  $\mathsf{BATE}$.
 \begin{table}
\scriptsize
\centering
\caption{Scheduled results of different schemes.}\label{testbed-1}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|l|l|l|l|ll} \hline
\setlength{\tabcolsep}{10pt}
{Service}&\multicolumn{1}{|c|}{paths}&\multicolumn{1}{|c|}{$\mathsf{BATE}$}&\multicolumn{1}{|c|}{TEAVAR}&\multicolumn{1}{|c|}{FFC}\\
\hline
&{DC1$\to$DC2$\to$DC3}&0&500&0\\
{Service-1}&{DC1$\to$DC4$\to$DC3}&1000&500&250\\
(99.5\%)&{DC1$\to$DC2$\to$DC5$\to$DC4$\to$DC3}&0&0&0\\
&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&0&0&0\\
\hline
&{DC1$\to$DC4}&0&250&0\\
{Service-2}&{DC1$\to$DC2$\to$DC5$\to$DC4}&0&0&0\\
(99.9\%)&{DC1$\to$DC2$\to$DC3$\to$DC4}&500&0&250\\
&{DC1$\to$DC6$\to$DC5$\to$DC4}&0&250&250\\
\hline
&{DC1$\to$DC2$\to$DC5}&500&500&750\\
{Service-3}&{DC1$\to$DC4$\to$DC5}&0&250&0\\
(95\%)&{DC1$\to$DC6$\to$DC5}&1000&750&750\\
&{DC1$\to$DC2$\to$DC3$\to$DC4$\to$DC5}&0&0&0\\
%&&&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&{750}\\
%&&&{DC1$\to$DC2$\to$DC3}&{0}\\
%&&&{DC1$\to$DC4$\to$DC3}&{0}\\
%{service-1}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC2$\to$DC3}&{750}\\
%(95\%)&&&{DC1$\to$DC4$\to$DC3}&{750}\\
%&&\multirow{2}{*}{{SWAN}}&{DC1$\to$DC2$\to$DC3}&{1000}\\
%&&&{DC1$\to$DC4$\to$DC3}&{500}\\
%\hline
%&\multirow{6}{*}{500}&\multirow{2}{*}{{$\mathsf{BATE}$}}&{DC1$\to$DC4}&{250}\\
%&&&{DC1$\to$DC2$\to$DC3$\to$DC4}&{250}\\
%{service-2}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC4}&{250}\\
%(99.99\%)&&&{DC1$\to$DC6$\to$DC5$\to$DC4}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC4}&{500}\\
%\hline
%&\multirow{4}{*}{500}&{{$\mathsf{BATE}$}}&{DC1$\to$DC6$\to$DC5}&{500}\\
%{service-3}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC6$\to$DC5}&{250}\\
%(90\%)&&&{DC1$\to$DC2$\to$DC5}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC6$\to$DC5}&{500}\\
\hline
\end{tabular}
\end{table}
We now test the performance under a simple private cloud example, where three services are deployed and all admitted.
Service-1 is from DC1 to DC3, Service-2 is from DC1 to DC4 and Service-3 is from DC1 to DC5.
Their bandwidth demands are 1000Mbps, 500Mbps and 1500Mbps, respectively.
Assume the availability targets of Service-1 , Service-2 and Service-3 are  99.5\%, 99.9\% and 95\%, respectively.
All services last 100s and each experiment repeats 100 times,  where the error bars paints the maximal, minimal and mean value.
$\mathsf{BATE}$-WT refers $\mathsf{BATE}$ without failure recovery.

Figure \ref{e1}(a) shows the bandwidth-based availability which is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%.
We can see that all services can reach their availability targets under $\mathsf{BATE}$, while Service-1 fails under FFC and Service-2 fails under both TEAVAR and FFC.
To explore the reason, we show the scheduled results of the three schemes in TABLE \ref{testbed-1}:  
(1) FFC reserves too much bandwidth to protect routing and service1 is unable to gain enough bandwidth;
(2) $\mathsf{BATE}$ abandons link L4 for Service-2, while TEAVAR adopts it.
According to the link failure times shown in Figure \ref{e1}(b), we can see that most failures are from link L4 in our experiment.
Although TEAVAR considers link failure probability, it ignores the availability targets of different services.
Therefore, Service-3 gains redundant bandwidth and affects Service-2 finally.
%During L4 failure, service2 is unable to gain enough bandwidth. 
%and it will take much time for the controller to retrieve from congestion.
%All links are up under normal circumstances and the probability of this scenario is 98.9\%.
%We now consider a scenario in which DC4-DC5 link fails and other links are up.
%The probability of this failure scenario is about 1\%, which is about 10 $\times$ larger than the probability sum of other failure scenarios.
%We disable the link between DC4 and DC5 at $t=0.2s$ to produce this scenario.
%Figure \ref{e1}(c) shows aggregate bandwidth from DC1 to DC3.
%We can see SWAN drops about 33\% bandwidth between 0.2s and 1.1s.
%The result of service1 is similar.
Data loss mainly comes from congestion and blackhole, where congestion losses are always link oversubscribed and blackhole losses occur during the time between a link fails and ingress switch rescale.
Figure \ref{e1}(c) demonstrates $\mathsf{BATE}$ and FFC performs better than   $\mathsf{BATE}$-WT  and TEAVAR for data losses ratio.
Data losses of Service-2 under TEAVAR is high due to Link L4 failings.
$\mathsf{BATE}$-WT performs worse than the other three schemes, because it takes much time to derive new resource allocation when network fails and the events time of  $\mathsf{BATE}$-WT shown in Figure \ref{e1}(d) just prove this.
%We can see that $\mathsf{BATE}$-1 and FFC performs better than   $\mathsf{BATE}$-2  and TEAVAR.
%The losses of TEAVAR mainly comes from link $L4$ failure which is adopt by Service-2.
%When L3 fails, DC1 and DC4 take about 0.4s to detect the failure.
%$\mathsf{BATE}$-1 can  rescale traffic with the backup allocation results, therefore, packet losses will stop immediately.
%Control messages distributing and switch updating take about 0.3s, while the most time-consuming operation is TE computation which takes about 1s, 
%therefore, $\mathsf{BATE}$-2 performs relatively worse than other schemes.
%$\mathsf{BATE}$ considers link failure probability as well as the diverse demands of services \textit{proactively}, as a result, the time consuming events shown in Figure  \ref{e1}(c) rarely happens.

>>>>

We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 miniutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes and is repeated for 50 times, 
where link failures occur probabilistically,

%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
%Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.
\textit{Admission control.} We evaluate how demands can be correctly admitted by $\mathsf{BATE}$, 
comparing with both the optimal admission strategy, 
and a strategy that assumes a \textit{fixed} bandwith allocation for demands that have already been admitted, which is effectively step (1) in $\mathsf{BATE}$.
Figure \ref{e2}(a) demonstrates that $\mathsf{BATE}$ performs closely to the optimal strategy, 
i.e., the false rejection ratio is at most 1\%, while the \textit{fixed} algorithm 
rejects least 10$\times$ more admissible demands. 
%This is because $\mathsf{BATE}$ fully considers the availability diversity of tenants.
%In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate.

\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwith availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in every second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfication, under 
different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
To further illustrate the difference in their mechanisms, 
we plot in Figure \ref{e2}(c), for each algorithm, the ratio of the allocated bandwidth 
to the demanded bandwidth. 
The cdf curve shows that FFC is too conservative in bandwidth allocation, 
and fails to allocate proper bandwidth in almost 60\% time.   
On the other hand, although TEAVAR provides bandwidth fairly well, 
it ignores the diverse availability requirements of different users, 
and achieves a lower satisfication ratio than $\mathsf{BATE}$.

\textit{Failure Recovery} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(d) plots the overall profit $\mathsf{BATE}$, FFC and TEAVAR can achieve for admitted demands, under three different admission control strategies, i.e., fixed, BATE-AD (which is the strategy $\mathsf{BATE}$ uses) and optimal. 
\textbf{TBD: This is because $\mathsf{BATE}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.}
Figure \ref{e2}(e) further depicts the fraction of profit loss caused by SLA violations, where the baseline for each algorithm is the profit it can achieve when no failures occur. 
\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation, as indicated in Figure \ref{e2}(c) earlier.

@@

%In this part we will perform experiments on our testbed to evaluate the performance of  $\mathsf{BATE}$.
 \begin{table}
\scriptsize
\centering
\caption{Scheduled results of different schemes.}\label{testbed-1}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|l|l|l|l|ll} \hline
\setlength{\tabcolsep}{10pt}
{Service}&\multicolumn{1}{|c|}{paths}&\multicolumn{1}{|c|}{$\mathsf{BATE}$}&\multicolumn{1}{|c|}{TEAVAR}&\multicolumn{1}{|c|}{FFC}\\
\hline
&{DC1$\to$DC2$\to$DC3}&0&500&0\\
{Service-1}&{DC1$\to$DC4$\to$DC3}&1000&500&250\\
(99.5\%)&{DC1$\to$DC2$\to$DC5$\to$DC4$\to$DC3}&0&0&0\\
&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&0&0&0\\
\hline
&{DC1$\to$DC4}&0&250&0\\
{Service-2}&{DC1$\to$DC2$\to$DC5$\to$DC4}&0&0&0\\
(99.9\%)&{DC1$\to$DC2$\to$DC3$\to$DC4}&500&0&250\\
&{DC1$\to$DC6$\to$DC5$\to$DC4}&0&250&250\\
\hline
&{DC1$\to$DC2$\to$DC5}&500&500&750\\
{Service-3}&{DC1$\to$DC4$\to$DC5}&0&250&0\\
(95\%)&{DC1$\to$DC6$\to$DC5}&1000&750&750\\
&{DC1$\to$DC2$\to$DC3$\to$DC4$\to$DC5}&0&0&0\\
%&&&{DC1$\to$DC4$\to$DC5$\to$DC2$\to$DC3}&{750}\\
%&&&{DC1$\to$DC2$\to$DC3}&{0}\\
%&&&{DC1$\to$DC4$\to$DC3}&{0}\\
%{service-1}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC2$\to$DC3}&{750}\\
%(95\%)&&&{DC1$\to$DC4$\to$DC3}&{750}\\
%&&\multirow{2}{*}{{SWAN}}&{DC1$\to$DC2$\to$DC3}&{1000}\\
%&&&{DC1$\to$DC4$\to$DC3}&{500}\\
%\hline
%&\multirow{6}{*}{500}&\multirow{2}{*}{{$\mathsf{BATE}$}}&{DC1$\to$DC4}&{250}\\
%&&&{DC1$\to$DC2$\to$DC3$\to$DC4}&{250}\\
%{service-2}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC4}&{250}\\
%(99.99\%)&&&{DC1$\to$DC6$\to$DC5$\to$DC4}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC4}&{500}\\
%\hline
%&\multirow{4}{*}{500}&{{$\mathsf{BATE}$}}&{DC1$\to$DC6$\to$DC5}&{500}\\
%{service-3}&&\multirow{2}{*}{{TEAVAR}}&{DC1$\to$DC6$\to$DC5}&{250}\\
%(90\%)&&&{DC1$\to$DC2$\to$DC5}&{250}\\
%&&{{SWAN}}&{DC1$\to$DC6$\to$DC5}&{500}\\
\hline
\end{tabular}
\end{table}

Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
Another factor we must pay attention into is the

%During L4 failure, service2 is unable to gain enough bandwidth. 
%and it will take much time for the controller to retrieve from congestion.
%All links are up under normal circumstances and the probability of this scenario is 98.9\%.
%We now consider a scenario in which DC4-DC5 link fails and other links are up.
%The probability of this failure scenario is about 1\%, which is about 10 $\times$ larger than the probability sum of other failure scenarios.
%We disable the link between DC4 and DC5 at $t=0.2s$ to produce this scenario.
%Figure \ref{e1}(c) shows aggregate bandwidth from DC1 to DC3.
%We can see SWAN drops about 33\% bandwidth between 0.2s and 1.1s.
%The result of service1 is similar.
\textbf{TBD:Data loss mainly comes from congestion and blackhole, where congestion losses are always link oversubscribed and blackhole losses occur during the time between a link fails and ingress switch rescale.
Figure \ref{e1}(c) demonstrates $\mathsf{BATE}$ and FFC performs better than   $\mathsf{BATE}$-WT  and TEAVAR for data losses ratio.
Data losses of Service-2 under TEAVAR is high due to Link L4 failings.
$\mathsf{BATE}$-WT performs worse than the other three schemes, because it takes much time to derive new resource allocation when network fails and the events time of  $\mathsf{BATE}$-WT shown in Figure \ref{e1}(d) just prove this.}
%We can see that $\mathsf{BATE}$-1 and FFC performs better than   $\mathsf{BATE}$-2  and TEAVAR.
%The losses of TEAVAR mainly comes from link $L4$ failure which is adopt by Service-2.
%When L3 fails, DC1 and DC4 take about 0.4s to detect the failure.
%$\mathsf{BATE}$-1 can  rescale traffic with the backup allocation results, therefore, packet losses will stop immediately.
%Control messages distributing and switch updating take about 0.3s, while the most time-consuming operation is TE computation which takes about 1s, 
%therefore, $\mathsf{BATE}$-2 performs relatively worse than other schemes.
%$\mathsf{BATE}$ considers link failure probability as well as the diverse demands of services \textit{proactively}, as a result, the time consuming events shown in Figure  \ref{e1}(c) rarely happens.
